Using Incremental Many-to-One Queries to Build a Fast and Tight Heuristic for A* in Road Networks

### 2021-11-15 paper/ch_potentials.tex
Figure descriptions

\bibliographystyle{plainurl} % the mandatory bibstyle

@@

\begin{figure}
\centering
\includegraphics[width=.6\columnwidth]{fig/searchspace_st.png}
\caption{Nodes explored by A*. Color indicates the node removal order from the queue. Blue was removed first. Next is green. Red was removed last.}
\label{img:search-space}
\end{figure}

@@

\draw[dashed] (4) -- (6);
\draw[dashed] (6) -- (8);
\end{tikzpicture}
\caption{
Solid lines are edges in $G$. Dotted lines are shortcuts. Red is shortest $st$-path in $G$. Blue is equaly long up-down $st$-path in $G^+$. $m$ is the mid node.
}
\label{fig:ch}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{fig/lazy_rphast_inc.pdf}
\caption{
Average running times of incremental Lazy RPHAST while querying $|S| = 2^{14}$ from a ball of varying size $|B|$ on OSM Germany excluding selection times.
The upper figure contains the total elapsed running time.
The lower figure contains the averaged running time per source, i.e. $y/x$ from the upper figure.
Note the different y-axis scales and units.
}\label{fig:lazy_rphast_inc}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{fig/lazy_rphast_many_to_one_both.pdf}
\caption{
Running times of (C)CH-based Lazy RPHAST for many-to-one queries with $|S| = 2^{14}$ sources picked from a ball of varying size $|B|$.
The running time includes the selection and the time to compute all distances.
}\label{fig:many_to_one}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{fig/scaled_weights.pdf}
\caption{
Running times on a logarithmic scale for queries on OSM Ger with scaled edge weights $w_q = \alpha \cdot w_\ell$.
The boxes cover the range between the first and third quartile.
The band in the box indicates the median, the diamond the mean.
The whiskers cover 1.5 times the interquartile range.
All other running times are indicated as outliers.
}\label{fig:scaled_weights}
\end{figure}

>>>>

@@

\begin{figure}
\centering
\includegraphics[width=.6\columnwidth]{fig/searchspace_st.png}
\caption{Nodes explored by A*. Color indicates the node removal order from the queue. Blue was removed first. Next is green. Red was removed last.}
\label{img:search-space}
\Description[A map where nodes visited by A* are marked.]{
A map of Karlsruhe where nodes visited by A* are marked.
The shape of the area with the visited nodes is similar to a drop.
The source node roughly lies in the center of the drop, the target node at the tip.
}
\end{figure}

@@

\draw[dashed] (4) -- (6);
\draw[dashed] (6) -- (8);
\end{tikzpicture}
\caption{
Solid lines are edges in $G$. Dotted lines are shortcuts. Red is shortest $st$-path in $G$. Blue is equaly long up-down $st$-path in $G^+$. $m$ is the mid node.
}
\label{fig:ch}
\Description[Nodes and edges of a shortest path in the original graph and the corresponding path in the augmented graph.]{
Nodes and edges of a shortest path in the original graph and the corresponding path in the augmented graph.
The y-position on the figure indicates the rank of each node.
Where the original shortest path down and then up, a shortcut edge connects the two higher nodes.
The path in the augmented graph goes only up and then down.
}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{fig/lazy_rphast_inc.pdf}
\caption{
Average running times of incremental Lazy RPHAST while querying $|S| = 2^{14}$ from a ball of varying size $|B|$ on OSM Germany excluding selection times.
The upper figure contains the total elapsed running time.
The lower figure contains the averaged running time per source, i.e. $y/x$ from the upper figure.
Note the different y-axis scales and units.
}\label{fig:lazy_rphast_inc}
\Description{
Two line graphs with each eight lines for different ball sizes and algorithms.
The x-axis in both graphs is the number of nodes that were queried up to that point in the incremental query.
In each graph, all lines have a similar shape and appear as scaled variants of each other.
The bigger the ball size the slower the whole algorithm.
The CCH based variant is somewhat slower for the most part.
Only for small ball sizes it is marginally faster when computing distances for more then 4096 sources.
When the ball is the entire graph, the CH based variant takes around 2.5ms for the first 512 sources, 5ms for 2048 sources and 25ms for 16384 sources.
Conversely, the average time per query is around 100mus for the first few queries, then drops to around 5mus after 512 sources, down to 2mus after 16384 sources.
For the smallest ball size of 16384, everything is 1.5 orders of magnitude faster.
}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{fig/lazy_rphast_many_to_one_both.pdf}
\caption{
Running times of (C)CH-based Lazy RPHAST for many-to-one queries with $|S| = 2^{14}$ sources picked from a ball of varying size $|B|$.
The running time includes the selection and the time to compute all distances.
}\label{fig:many_to_one}
\Description{
A double logarithmic line plot with four lines with similar shapes and absolute values.
Running times for both algorithms and graphs with a ball size of 16384 is around 1ms.
For a ball size of 2 to the 20 CH based variants need 10ms and CCH based variants slightly more.
For a ball size of 2 to the 24 CH based variants are at 30ms and CCH based variants slightly above 40ms.
}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{fig/scaled_weights.pdf}
\caption{
Running times on a logarithmic scale for queries on OSM Ger with scaled edge weights $w_q = \alpha \cdot w_\ell$.
The boxes cover the range between the first and third quartile.
The band in the box indicates the median, the diamond the mean.
The whiskers cover 1.5 times the interquartile range.
All other running times are indicated as outliers.
}\label{fig:scaled_weights}
\Description{Fully described in the text.}
\end{figure}
